Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-04-12 papers/ms.tex
update ms

Our adopted approach was as follows.  Given an initial guess for the
transit ephemeris from the \texttt{q1\_q17\_dr25} analysis
\citep{thompson_planetary_2018}, the light curve was first trimmed to
a local window around each transit, spanning $\pm 3\times t_{14}$.
The local out-of-transit points were then fitted with a fourth-order
polynomial, which was then divided out from the light curve.  The
resulting flattened transits were then fitted with a planetary transit
under the assumption of quadratic limb darkening.  Our model therefore
included 8 free parameters for the transit ($\{P, t_0, \log R_{\rm
p}/R_\star, b, u_1 ,u_2, R_\star, \log g\}$), 2 free parameters for
the light curve normalization and a white noise jitter ($\{\langle f
\rangle, \sigma_f \}$), and an additional 5 implicit parameters per
transit through the polynomial.

We fitted the models using \texttt{exoplanet}
\citep{exoplanet:exoplanet}.  We assumed a Gaussian likelihood, and
sampled using \texttt{PyMC3}'s No-U-Turn Sampler
\citep{hoffman_no-u-turn_2014}, after having initialized using the
maximum {\it a posteriori} (MAP) model.  We used the
\citet{gelman_inference_1992} statistic ($\hat{R}$) as our convergence
diagnostic.  The resulting fits are shown in the lower panels of
Figure~\ref{fig:planets}, and the important derived parameters are in
Table~\ref{tab:sysparams}.  The set of full parameters with their
priors are given in Appendix~\ref{app:transit}.

One weakness of our fitting approach is that we have fixed 5 implicit
parameters per individual transit to their MAP values to remove the
stellar variability signal.  An alternative could be to fit the
planetary transits simultaneously with the starspot-induced
variability using, say, a quasiperiodic Gaussian process (GP).  We
explored this approach, but found that it required careful fine-tuning
of the hyperparameter priors, otherwise the GP would tend to
incorporate variability that was not part of the transit, even if it
was short-term variability attributable to flares, or simply
instrumental noise.  This failure mode is somewhat pernicious, in that
it yields an ill-founded sense of confidence in an ``overly clean''
transit model fit.  While our model is simpler, it has the benefit
that the white noise jitter never trades off with any parameter
equivalent to a damping timescale for the coherence of the GP.  It is
also computationally efficient, and it captures the planetary
parameters about which we care the most.

@@

In the future, it may be possible to obtain independent evidence for
the Cep-Her planets to directly confirm their planetary nature.  The
most likely path would be through transit observations using a
high-resolution spectrograph.  In
the interim, it is of interest whether the transit signals could be
astrophysical false positives, or whether they can be argued to be
planetary on a statistical basis.  We adopt the Bayesian framework
implemented in \texttt{VESPA} for this purpose
\citep{morton_efficient_2012,vespa_2015}.  Briefly summarized, the
priors in \texttt{VESPA} take as given the binary star occurrence rate
from \citet{raghavan_survey_2010}, direction-specific star counts from
\citet{girardi_star_2005}, and planet occurrence rates as described by
\citet[][Section~3.4]{morton_efficient_2012}.  The likelihoods are
then evaluated by forward-modeling a synthetic population of eclipsing
bodies for each possible astrophysical model class, in which each
population member has a particular trapezoidal eclipse depth, total
duration, and ingress duration.  These summary statistics are then
compared against the actual photometric data to evaluate the
probabilities of false positive scenarios such as foreground eclipsing
binaries, hierarchical eclipsing binaries, and background eclipsing
binaries.

\paragraph{Kepler-1643}
Kepler-1643~b (KOI-6186.01) was already validated as a transiting
planet by \citet{morton_false_2016}, who found a probability for any
of the aforementioned false positive scenarios of 9$\times$10$^{-6}$.
Repeating the calculation with our own stellar-variability correction
and the new NIRC2 imaging constraints, we find ${\rm FPP} =
6\times10^{-9}$, where the improvement is due to the new NIRC2
contrast curves.  Figure~\ref{fig:planets} shows the justification:
the transit is flat and has a high S/N ($\approx 47$).  The shape is
therefore difficult to reproduce with eclipsing binary models.

Intriguingly, Kepler-1643 formally failed one of the centroid shift
tests (see the \texttt{q1\_q17\_dr25\_koi} data release): the angular
distance between the target star's catalog position and the position
of the transiting source was measured as $1\farcs0$ at 4.4-$\sigma$.
The reports show however that two outlying quarters (2 and 6) drive
the offset -- the centroid locations from the other Kepler quarters
are consistent at $\lesssim 0\farcs4$.  Nonetheless, this is an
instructive exercise in how stellar variability complicates
centroid-based vetting tests.  The centroid shifts measured by these
tests are determined from the in- and out-of-transit flux-weighted
centroids.  For stars with significant spot-induced variability there
is no static baseline in either the in- or out-of-transit phases.

>>>>

We fitted the data as follows.  Given an initial guess for the transit
ephemeris from \citet{thompson_planetary_2018}, we first trimmed the
light curve to a local window around each transit that spanned three
transit durations before and after each mid-transit time.  The
out-of-transit points in each local window were then fitted with a
fourth-order polynomial, which was then divided out from the light
curve.  The resulting flattened transits were then fitted with a
planetary transit under the assumption of quadratic limb darkening.
Our model therefore included 8 free parameters for the transit ($\{P,
t_0, \log R_{\rm p}/R_\star, b, u_1 ,u_2, R_\star, \log g\}$), 2 free
parameters for the light curve normalization and a white noise jitter
($\{\langle f \rangle, \sigma_f \}$), and an additional 5 implicit
parameters for each transit.

We fitted the models using \texttt{exoplanet}
\citep{exoplanet:exoplanet}.  We assumed a Gaussian likelihood, and
sampled using \texttt{PyMC3}'s No-U-Turn Sampler
\citep{hoffman_no-u-turn_2014}, after having initialized to the the
maximum {\it a posteriori} (MAP) model.  We used the
\citet{gelman_inference_1992} statistic ($\hat{R}$) as our convergence
diagnostic.  The resulting fits are shown in the lower panels of
Figure~\ref{fig:planets}, and the important derived parameters are in
Table~\ref{tab:sysparams}.  The set of full parameters with their
priors are given in Appendix~\ref{app:transit}.

One weakness of our approach is that we have fixed 5 implicit
parameters per individual transit to their MAP values to remove the
stellar variability signal.  An alternative could be to fit the
planetary transits simultaneously with the starspot-induced
variability using, say, a quasiperiodic Gaussian process (GP).  We
explored this approach, but found that it required careful fine-tuning
of the hyperparameter priors, otherwise the GP would tend to
incorporate variability that was not part of the transit, even if it
was short-term variability attributable to flares or instrumental
noise.  This failure mode is pernicious, in that it yields an
ill-founded sense of confidence in an ``overly clean'' transit model
fit.  Our model is simpler, and it has the benefit that the white
noise jitter never trades off with any parameter equivalent to a
damping timescale for the coherence of the GP.  It is also
computationally efficient, and it captures the planetary parameters
about which we care the most.

@@

In the future, it may be possible to obtain independent evidence for
the Cep-Her planets to directly confirm their planetary nature, for
instance through transit observations using a high-resolution
spectrograph.  For now, it is of interest whether the transit signals
might be astrophysical false positives, or whether they can be argued
to be planetary on a statistical basis.  We adopt the Bayesian
framework implemented in \texttt{VESPA} to assess the relevant
probabilities \citep{morton_efficient_2012,vespa_2015}.  Briefly
summarized, the priors in \texttt{VESPA} assume the binary star
occurrence rate from \citet{raghavan_survey_2010}, direction-specific
star counts from \citet{girardi_star_2005}, and planet occurrence
rates as described by \citet[][Section~3.4]{morton_efficient_2012}.
The likelihoods are then evaluated by forward-modeling a synthetic
population of eclipsing bodies for each astrophysical model class, in
which each population member has a known trapezoidal eclipse depth,
total duration, and ingress duration.  These summary statistics are
then compared against the actual photometric data to evaluate the
probabilities of false positive scenarios such as foreground eclipsing
binaries, hierarchical eclipsing binaries, and background eclipsing
binaries.

\paragraph{Kepler-1643}
Kepler-1643~b (KOI-6186.01) was already validated as a transiting
planet by \citet{morton_false_2016}, who found a probability for any
of the aforementioned false positive scenarios of 9$\times$10$^{-6}$.
Repeating the calculation with our own stellar-variability correction
and the new NIRC2 imaging constraints, we find ${\rm FPP} =
6\times10^{-9}$.  Figure~\ref{fig:planets} shows the justification:
the transit is flat and has a high S/N ($\approx 47$).  The shape is
therefore nearly impossible to reproduce with eclipsing binary models.

Intriguingly, Kepler-1643 formally failed one of the data validation
centroid shift tests (see the \texttt{q1\_q17\_dr25\_koi} data
release): the angular distance between the target star's catalog
position and the position of the transiting source was measured as
$1\farcs0$ at 4.4-$\sigma$.  The reports show however that two
outlying quarters (2 and 6) drive the offset -- the centroid locations
from the other Kepler quarters are consistent at $\lesssim 0\farcs4$.
Nonetheless, this is an instructive exercise in how stellar
variability complicates centroid-based vetting tests.  The centroid
shifts measured by these tests are determined from the in- and
out-of-transit flux-weighted centroids.  For stars with significant
spot-induced variability there is no static baseline in either the in-
or out-of-transit phases.
